\documentclass{article}
\usepackage{enumitem}% http://ctan.org/pkg/enumitem
\begin{document}
\bibliography{} 
\bibliographystyle{ieeetr}
\begin{enumerate}[label={[\arabic*]}]
  \item Yazan Boshmaf, Konstantin Beznosov, and Matei Ripeanu. Graphbased sybil detection in social and information systems. In Advances in Social Networks Analysis and Mining (ASONAM), 2013 IEEE/ACM International Conference on, IEEE, 2013.
  \item  Md Sazzadur Rahman, Ting-Kai Huang, Harsha V Madhyastha, and Michalis Faloutsos. Efficient and scalable socware detection in online social networks. In USENIX Security Symposium, pages 663–678, 2012.
  \item  Zhi Yang, Christo Wilson, Xiao Wang, Tingting
        Gao, Ben Y Zhao, and Yafei Dai. Uncovering social
        network sybils in the wild. ACM Transactions on
        Knowledge Discovery from Data (TKDD), 2014.
  \item ] Md Sazzadur Rahman, Ting-Kai Huang, Harsha V. Madhyastha,
and Michalis Faloutsos. Frappe: Detecting malicious facebook
applications. In Proceedings of the 8th International Conference on
Emerging Networking Experiments and Technologies, CoNEXT ’12,
pages 313–324, New York, NY, USA, 2012. ACM.
  \item Bimal Viswanath, M Ahmad Bashir, Mark Crovella, Saikat Guha,
MSR India, Krishna P Gummadi, Balachander Krishnamurthy, and
Alan Mislove. Towards detecting anomalous user behavior in
online social networks. In Proceedings of the 23rd USENIX Security
Symposium (USENIX Security), 2014.
  \item Manuel Egele, Gianluca Stringhini, Christopher Kruegel, and Giovanni
Vigna, Compa- detecting compromised accounts on social
networks. In NDSS, 2013.
  \item Phil McKenna. The rise of cyberbullying. New
Scientist, 195(2613):26–27, 2007.
\item Onur Varol, Emilio Ferrara, Clayton A. Davis, Filippo Menczer, Alessandro Flammini, Online Human-Bot Interactions: Detection, Estimation, and Characterization.
\item Rodrigo Augusto Igawa, Alex Marino Gonçalves de Almeida, Bruno Bogaz Zarpelão, Sylvio Barbon Jr, Recognition of Compromised Accounts on Twitter, XI Brazilian Symposium on Information System, Goiˆania, GO, May 26-29, 2015.
\item Meike Nauta, Detecting Hacked Twitter Accounts by Examining
Behavioural Change using Twitter Metadata, IEEE, 2017.
\item Ting-Kai Huang, Md Sazzadur Rahman, Harsha V
Madhyastha, Michalis Faloutsos, and Bruno Ribeiro. An
analysis of socware cascades in online social networks.
In Proceedings of the 22nd international conference on
World Wide Web, pages 619–630. International World
Wide Web Conferences Steering Committee, 2013.
\item Ralph Gross and Alessandro Acquisti. Information
revelation and privacy in online social networks. In
Proceedings of the 2005 ACM workshop on Privacy in
the electronic society, pages 71–80. ACM, 2005.
\item Michael Fire, Roy Goldschmidt, and Yuval Elovici.
Online social networks- threats and solutions. 2013.
\item Phil McKenna. The rise of cyberbullying. New
Scientist, 195(2613):26–27, 2007.
\item Zhi Yang, Christo Wilson, Xiao Wang, Tingting
Gao, Ben Y Zhao, and Yafei Dai. Uncovering social
network sybils in the wild. ACM Transactions on
Knowledge Discovery from Data (TKDD), 2014.
\item Leyla Bilge, Thorsten Strufe, Davide Balzarotti, and
Engin Kirda. All your contacts are belong to us
automated identity theft attacks on social networks. In
Proceedings of the 18th international conference on
World wide web, pages 551–560. ACM, 2009.
\item L. Ablon, M. C. Libicki, and A. A. Golay. Markets
for Cybercrime Tools and Stolen Data: Hackers’
Bazaar. RAND Corporation, Santa Monica, CA,
2014.
\item S.-A. Bahrainian and A. Dengel. Sentiment analysis
and summarization of twitter data. In Computational
Science and Engineering (CSE), 2013 IEEE 16th
International Conference on, pages 227–234. IEEE,
2013.
\item S. Y. Bhat and M. Abulaish. Community-based
features for identifying spammers in online social
networks. In Proceedings of the 2013 IEEE/ACM
International Conference on Advances in Social Networks Analysis and Mining, pages 100–107. ACM,
2013.
\item S. Yardi, D. Romero, G. Schoenebeck, and D. Boyd.
Detecting spam in a twitter network. First Monday,
15(1), 2010.
\item K. Thomas, F. Li, C. Grier, and V. Paxson.
Consequences of connectivity: Characterizing
account hijacking on twitter. Proceedings of the
ACM Conference on Computer and
Communications Security, pages 489–500, 2014.
\item C. Chen, J. Zhang, X. Chen, Y. Xiang, and
W. Zhou. 6 million spam tweets: A large ground
truth for timely twitter spam detection. IEEE
International Conference on Communications,
2015-September:7065–7070, 2015.\item E. Zangerle and G. Specht. ”sorry, i was hacked” a
classification of compromised twitter accounts.
Proceedings of the ACM Symposium on Applied
Computing, pages 587–593, 2014.
\end{enumerate}
\end{document}